Technical Report

### 2018-06-22 fully-abstract-comp/technical-report.tex
Clarify a proof slightly.

\begin{lemma}
  \label{lem:lrvtrusted-not-nequal-lrvuntrusted}
  If $n > 0$
  then
  $\lrv \not\nequal \lrvg{\trusted}$
\end{lemma}
\begin{proof}
  Take $\sigma \in (\gsigrets\cup \gsigcloss)$, $w = \seal{\sigma,\sigma,\sigma}$, $W$ such that $W(r) = \codereg{\sigrets,\sigcloss,\code,\gc}$, $\sigrets \subseteq \gsigrets$, $\sigcloss\subseteq \gsigcloss$, $\dom(\code) \subseteq \ta$ and $W$ empty otherwise.
  Then we have that $\npair[0]{(w,w)}\in \lrvg{\trusted}(W)$ but not $\npair[0]{(w,w)}\in\lrv(W)$.
\end{proof}

>>>>

\begin{lemma}
  \label{lem:lrvtrusted-not-nequal-lrvuntrusted}
  If $n > 0$ then $\lrv \not\nequal \lrvg{\trusted}$.
\end{lemma}
\begin{proof}
  Take $\sigma \in (\gsigrets\cup \gsigcloss)$, $w = \seal{\sigma,\sigma,\sigma}$, $W$ such that $W(r) = \codereg{\sigrets,\sigcloss,\code,\gc}$, $\sigrets \subseteq \gsigrets$, $\sigcloss\subseteq \gsigcloss$, $\sigma \in (\sigrets\cup\sigcloss)$, $\dom(\code) \subseteq \ta$ and $W$ empty otherwise.
  Then we have that $\npair[0]{(w,w)}\in \lrvg{\trusted}(W)$ but not $\npair[0]{(w,w)}\in\lrv(W)$.
\end{proof}
